Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-20 Draft/contributions.tex
contributions.tex: modified caption of table

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Order & $\mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
        \hline
        \hline
        $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
%         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Order & $\mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
        \hline
        \hline
        $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
%         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$, obtained with full matrix elements.
    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
\end{table}
